% ■ アブストラクトの出力 ■
%	◆書式：
%		begin{jabstract}〜end{jabstract}	：日本語のアブストラクト
%		begin{eabstract}〜end{eabstract}	：英語のアブストラクト
%		※ 不要ならばコマンドごと消せば出力されない。



% 日本語のアブストラクト
\begin{jabstract}

モバイルデバイスの進化と普及と共に文字入力の機会は増加している。
しかし現状スマートフォンを利用してる人々の
日本語入力IMEには大きな変化はみられない。
本研究では現状のモバイルデバイスに適した、
より早く面白い入力を可能にする日本語入力IME
「Rive日本語入力」を設計し実装した。
本システムにおける最大の特徴はコンテキストを用いた
候補単語の推薦を行うことである。
コンテキストと入力を関連付けると共に、
過去の全てのユーザーの入力データを利用することで
ユーザーの入力したいであろう単語を推測する。
ユーザーは意識することなく推薦候補単語を受け取り、
選択するだけで入力をすることができる。
本論文においては
開発した日本語入力IMEの設計や実装、
採用したユーザインタフェースを提示することで、
システムの有用性を述べる。
また本システムの課題やそれに対するアプローチを述べることで、
日本語入力IMEにおける本研究の意義を論ずる。

\end{jabstract}

% 英語のアブストラクト
\begin{eabstract}

We are increasing at an opportunity to input text
with evolution and the spread of mobile devices.
But smartphone user's inputting hardly changes in Japanese IME.
In this research, I designed and implemented Japanese IME:
"Rive Japanese Input" which enables the quick input
and interesting input of the user.
The biggest feature of this system is to recommend candidate words
from the context.
I connect input data with context and suppose the text
that the user want to input by using the past input data
of all users
The user receives recommendation candidate words unconsciously.
And he complete input only to choose words in recommendation
candidate words.
In this paper, I propose usability of this system by adopting
user interface and the implementation of Japanese IME which
I developed.
And I discuss importance of this study.

\end{eabstract}
